Adopting agile in the large: motivations, success factors and challenges

### 2014-04-22 journal/article.tex
Corrections for tables

        RQ1: Reason to change &
        Reasons to start the transformation (demand for shorter
        TTM\footnotemark[1]). \\

@@

\footnotetext[1]{Time To Market}

@@

\begin{table}[h]
    \begin{tabular}{ l r r }
        \toprule
        Code family    &  Codes  &  Quotations
        \\
        \midrule
        RQ1: Reason to change &        10 &   70 \\
		RQ2: Transformation process &  13 &  538 \\
		RQ3: Challenges &              39 &  307 \\
		RQ3: Success factors &         44 &  247 \\
		Investing in change  &          5 &  130 \\
		Practices &                    11 &  160 \\
		Contextual &                    8 &  167 \\
		Total &                       133 & 1440 \\
        \bottomrule
    \end{tabular}
    \caption{Number of codes and quotations per code family}
    \label{table:codecount}
\end{table}

@@

\begin{table}[bh]
    \begin{tabular}{ l r }
        \toprule
        Business area    &  Case organizations   \\
        \midrule
		Online services for consumers and business  &  9  \\
		Telecommunications                          &  7  \\
		Enterprise management                       &  5  \\
		Banking and financial services              &  4  \\
		Healthcare                                  &  3  \\
		IT services                                 &  2  \\
		Government                                  &  1  \\
		Information security                        &  1  \\
		Not specified                               & 10  \\
        \bottomrule
    \end{tabular}
    \caption{Business areas of case organizations in primary studies}
    \label{table:businessareas}
\end{table}

>>>>

        RQ1: Reason to change &
        Reasons to start the transformation (demand for faster delivery). \\

@@

@@

\begin{table}[h]
    \begin{tabular}{ l r r }
        \toprule
        Code family    &  Codes  &  Quotations
        \\
        \midrule
        RQ1: Reason to change &        31 &  124 \\
		RQ2: Transformation process &  16 &  580 \\
		RQ3: Challenges &              40 &  323 \\
		RQ3: Success factors &         44 &  260 \\
		Investing in change  &          5 &  137 \\
		Practices &                    11 &  170 \\
		Contextual &                    8 &  215 \\
		Total &                       155 & 1576 \\
        \bottomrule
    \end{tabular}
    \caption{Number of codes and quotations per code family}
    \label{table:codecount}
\end{table}

@@

\begin{table}[bh]
    \begin{tabular}{ l r }
        \toprule
        Business area    &  Case organizations   \\
        \midrule
		Online services for consumers and business  &  9  \\
		Telecommunications                          &  7  \\
		Enterprise management                       &  5  \\
		Banking and financial services              &  4  \\
		Healthcare                                  &  3  \\
		IT services                                 &  2  \\
		Government                                  &  1  \\
		Information security                        &  1  \\
		Not specified                               & 10  \\
        \midrule
		Total                                       & 42  \\
        \bottomrule
    \end{tabular}
    \caption{Business areas of case organizations in primary studies}
    \label{table:businessareas}
\end{table}
